---
title: "101BHW5"
author: "JING LI"
date: "3/1/2017"
output: pdf_document
---

8.1 

```{r}
#generator: D=ABC 

#defining relation: I=ABCD 

#aliases: A=BCD,B=ACD,C=ABD,D=ABC,AB=CD,AC=BD,AD=BC
A <- rep(c(-1,1),4)
B <- rep(c(-1,-1,1,1),2)
C <- c(rep(-1,4),rep(1,4))
D <- c(-1,1,1,-1,1,-1,-1,1)
yield <- c(90,72,87,83,99,81,88,80)
m1.aov <- aov(yield ~ factor(A)*factor(B)*factor(C)*factor(D)) 
summary(m1.aov)
```
```{r}
m1 <- lm(yield ~ A*B*C*D) 
2*coef(m1)[-1]
```
We can further reduce the model base on our preliminary results.
```{r}
m1.aov.red <- aov(yield~factor(A)+factor(B)+factor(C)+factor(A):factor(B)+factor(B):factor(C)) 
summary(m1.aov.red)
```
From the result, it seems that main effect A is the most effective factor here.


8.2 


```{r}
#generator: D=ABC 

#defining relation: I=ABCD 

#aliases: A=BCD,B=ACD,C=ABD,D=ABC,AB=CD,AC=BD,AD=BC

A.2 <- rep(c(-1,1),4)
B.2 <- rep(c(-1,-1,1,1),2)
C.2 <- c(rep(-1,4),rep(1,4))
D.2 <- c(-1,1,1,-1,1,-1,-1,1)
cracks <- c(7.037,16.867,13.876,17.273,11.846,4.368,9.36,15.653) 
m2.aov <- aov(cracks ~ factor(A.2)*factor(B.2)*factor(C.2)*factor(D.2))
summary(m2.aov)
```
```{r}
m2 <- lm(cracks ~ A.2*B.2*C.2*D.2) 
2*coef(m2)[-1]
```
We can further reduce the model base on our preliminary results.
```{r}
m2.aov.red <- aov(cracks~factor(A.2)+factor(B.2)+factor(C.2)+factor(D.2)+factor(A.2):factor(C.2)) 
summary(m2.aov.red)
```
Factors B and D appear to be more effective in this experiment, however the impact is not significant enough to make any inference.

8.4 
```{r}
#generators: D=AB, E=AC 

#defining relation: I = ABD = ACE = BCDE 

#aliases: A=BD=CE,B=AD=CDE,C=AE=BDE,D=AB=BCE,E=AC=BCD,BC=DE=ACD=ABE,CD=BE=ABC=ADE

A.4 <- rep(c(-1,1),4)
B.4 <- rep(c(-1,-1,1,1),2)
C.4 <- c(rep(-1,4),rep(1,4))
D.4 <- c(1,-1,-1,1,1,-1,-1,1)
E.4 <- c(1,-1,1,-1,-1,1,-1,1)
results <- c(6,9,35,50,18,22,40,63)
m3.aov <- aov(results~factor(A.4)*factor(B.4)*factor(C.4)*factor(D.4)*factor(E.4)) 
summary(m3.aov)         
```
```{r}
m3 <- lm(results ~ A.4*B.4*C.4*D.4*E.4) 
2*coef(m3)[-1]
```
We can further reduce the model base on our preliminary results.

```{r}
m3.aov.red <- aov(results ~ factor(A.4)+factor(B.4)+factor(C.4)+factor(D.4)) 
summary(m3.aov.red)
```
It seems that factor B is significant here. In other words, only B factor appears to have a great effect on the results.


8.11

a.

```{r}
# D=BE, E=AC
A.11 <- rep(c(-1,1),4)
B.11 <- rep(c(-1,-1,1,1),2)
C.11 <- c(rep(-1,4),rep(1,4))
D.11 <- c(-1,1,1,-1,1,-1,-1,1) 
E.11 <- c(1,-1,1,-1,-1,1,-1,1)
response <- c(23.2,16.9,16.8,15.5,23.8,23.4,16.2,18.1)
```

b.

```{r}
#defining relation: I=ACE=BDE=ABCD 
#aliases: A=CE=ABDE=BCD,B=ABCE=DE=ACD,C=AE=BCDE=ABD,D=ACDE=BE=ACD,E=AC=BD=ABCDE,AB=BCE=ADE=CD,AD=CDE=ABE=BC

```

c.

```{r}
m4 <- lm(response ~ A.11+B.11+C.11+D.11+E.11) 
2*coef(m4)[-1]
```

d.

```{r}
m4.aov <- aov(response ~ factor(A.11)+factor(B.11)+factor(C.11)+factor(D.11)+factor(E.11)) 

summary(m4.aov)
```

e.

```{r}
normalplot <- function(y, label=F,  n=length(y), fac.names=NULL, xlim=c(-2.2, 2.2), main="Normal Plot", ...)
  { # label the most singificant n effects
    m <- length(y)
    x <- seq(0.5/m, 1.0-0.5/m, by=1/m)
    x <-  qnorm(x)
    y <-  sort(y)
    qqplot(x, y, xlab="normal quantiles", ylab="effects",  xlim=xlim, main=main, ...)
    if(is.null(fac.names)) fac.names <-  names(y)
    else fac.names <-  rev( c(fac.names, rep("", length(y)-length(fac.names)) ) )
 
    ord=order(abs(y))
    if(label) for(i in ord[(m-n+1):m]) text(x[i]+.35,y[i], fac.names[i])  
  }

plot(m4.aov$residuals ~ m4$fitted.values)
normalplot(m4.aov$residuals) 
qqline(m4.aov$residuals)
```
The model seems to be adequate, there is no obvious violation of the assumptions.
