---
title: "101BHW1"
author: "JING LI"
date: "1/17/2017"
output: pdf_document
---

UID:604416262
SECTION:3A

Chapter 1 Problems: 1.3, 1.4, 1.8, 1.9
Chapter 2 Problems: 2.5, 2.9, 2.13, 2.15, 2.19, 2.20, 2.25, 2.28, 2.32

1.3. 

Step 1: Recognition of and statement of the problem- What is the growth of garden flowers under different conditions?
Step 2: Selection of the response variable-  growth of garden flowers
Step 3: Choice of factors, levels, and range-  
Design factors
Controllable
sunlight
water
fertilizer
soil condition
Uncontrollable
weather
temperature 
moisture
insect activity

1.4.

Step 1: Recognition of and statement of the problem- What is the effect on a patient's weight under a diet?
Step 2: Selection of the response variable-  the patient's weight 
Step 3: Choice of factors, levels, and range-  
Design factors
Controllable
diet
Uncontrollable
exercise 
mood
digestion efficiency

1.8. 
This allows the experimenter to obtain an estimate of experimental error, which is a basic unit of measurement to determine whether observed differences in the data are really statistically significant.

Also, if the sample mean is used to estimate the true mean response for one of the factor levels, then this allows for a more precise estimate of the parameter.

Helps to attain a more reliable estimate of the effect of each treatment.
One replication might not give us enough information to form a conclusion.

If we wish to test the effect of a new drug, we can randomly assign a control group and a experiment group. Multiple patients in the experiment group are replicates. If we measure one patient more than once, repetition results.


1.9. 
Can help average out the effects of irrelevant or unknown factors that may be present.It prevents subjective assignment.

2.5. 
(a) 
Z=(Xbar-mu)/(sd/sqrt(n))
```{r}
(31.2-30)/(1.2/sqrt(16))
pnorm(4,lower.tail = FALSE)
```
The 95% confidence interval does not contain the null, we will reject the null. There is evidence that mu is different from 30.

(b) 
Two-sided test. Because both mu>30 and mu<30 are considered as the alternative hypothesis.

(c) 
```{r}
31.2+qnorm(c(0.005,0.995))*(1.2/sqrt(16))
```

(d)
2.9.
(a)
```{r}
2.35/2.01
```
(b) 
Two sided test
(c) 
p<0.05 we reject the null. There is significant difference between the two sample mean.
(d) 
```{r}
2.35+qt(c(0.05,0.95), 18)*(2.35/2.01)
```

2.13. 
(a) 
SE=s/sqrt(n)
```{r}
0.4673*sqrt(25)
```
Yes, we can reject the null. Because this is a two-sided test, and p<0.025, there is evidence that mean is different from 91.
(b) 
This is a two-sided test.
(c) 
t=(x-mu)/(SE)
```{r}
(92.5805-90)/0.4673
pt(5.522149,24, lower.tail = FALSE)
```
P<0.025, we would still reject the null with a smaller p value.
(d) 
```{r}
92.5805-qt(c(0.995, 0.005),24)*0.4673
```
(e) 
p-value for the two-sided test is .002, so the one-sided p-value will be half as much. p=0.001


2.15. 
???(a)
Yes, the null can be rejected as 0.05 level. Because p-value<0.025, there is evidence that the two sample means are different.

(b) 
This is a two-sided test

(c) 
I would still reject the null, because the difference -4.33341 is further away from 0, ensuring that the p-value for that test would be even more significant

(d) 
I would also reject the null, because the p-value for the two-sided test is aleady significant, the one-sided p-value will only be half as much. 

(e) 
```{r}
(-2.33341)+qt(0.95,38, lower.tail = FALSE)*sqrt(1.71^2/20+2.48^2/20)
```

(f) 
```{r}
t <- ((-2.33341)-2)/sqrt(1.71^2/20+2.48^2/20)
pt(t,38)
```


2.19. 
```{r}
(1.96*(3/0.5))^2
```

2.20. 
(a) 
H0:mu=120 Ha:mu>120
(b) 
```{r}
sample1 <- c(108,124,124,106,115,138,163,159,134,139)
mean(sample1)
var(sample1)
(131-120)/sqrt(382/10)
pt(1.779758, 9,lower.tail = FALSE)
```
Since p-value>0.01, we fail to reject the null.

(c) 
```{r}
pt(1.779758, 9,lower.tail = FALSE)
```

(d)
```{r}
131+qt(c(0.005,0.995), 9)*sqrt(382/10)
```


2.25. 
```{r}
z<-(162.5-155.0-10)/sqrt(1.0/10+1.0/12)
qnorm(0.01, lower.tail = FALSE)
(162.5-155.0)+qnorm(c(0.005,0.995))*sqrt(1.0/10+1.0/12)
```
We fail to reject the null, there is little evidence indicating that the mean difference is greater than 10. They should not use plastic 1.


2.28  
(a) 
```{r}
f<-101.17/94.73
qf(0.025, 7,8)
pf(f,7,8)
```
P-value>0.025, we fail to reject the null, we can assume that the variances are equal.

(b) 
```{r}
Spooled <- ((8-1)*(101.17)+(9-1)*(94.73))/(8+9-2)
t<-(12.5-10.2)/sqrt(Spooled*(1/8+1/9))
pt(t,15)
```
P-value>0.025, we fail to reject the null.There is little evidence that the filtering device reduced the percentage of impurity significantly.

2.32. 
```{r}
y1 <- c(0.265,0.265,0.266,0.267,0.267,0.265,0.267,0.267,0.265,0.268,0.268,0.265)
mean(y1)
y2 <- c(0.264,0.265,0.264,0.266,0.267,0.268,0.264,0.265,0.265,0.267,0.268,0.269)
t.test(y1,y2, paired = TRUE)
```
p-value=0.674>0.025, there is no significant difference between the means.



