---
title: "101BHW4"
author: "JING LI"
date: "2/23/2017"
output: pdf_document
---

6.1
a.
```{r}
cg <- 22+31+25
a <- 32+43+29
b <- 35+34+50
ab <- 55+47+46
c <- 44+45+38
ac <- 40+37+36
bc <- 60+50+54
abc <- 39+41+47
A <- 1/12*(a-cg+ab-b+ac-c+abc-bc)
B <- 1/12*(b+ab+bc+abc-cg-a-c-ac)
C <- 1/12*(c+ac+bc+abc-cg-a-b-ab)
AB <- 1/12*(abc-bc+ab-b-ac+c-a+cg)
AC <- 1/12*(cg-a+b-ab-c+ac-bc+abc)
BC <- 1/12*(cg+a-b-ab-c-ac+bc+abc)
ABC <- 1/12*(abc-bc-ac+c-ab+b+a-cg)
c(A,B,C,AB,AC,BC,ABC)
```
The largest effects are for tool geometry(B), the cutting speed-cutting angle interaction(AC), and the cutting-angle(C).


b.
```{r}
A_F <- c(0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1)
B_F <- c(0,0,1,1,0,0,1,1,0,0,1,1,0,0,1,1,0,0,1,1,0,0,1,1)
C_F <- c(0,0,0,0,1,1,1,1,0,0,0,0,1,1,1,1,0,0,0,0,1,1,1,1)
rep <- c(22,32,35,55,44,40,60,39,31,43,34,47,45,37,50,41,25,29,50,46,38,36,54,47)
d1 <- data.frame(cbind(A_F,B_F,C_F), stringsAsFactors = TRUE)
m1 <- aov(rep ~ A_F*B_F*C_F, data = d1)
summary(m1)
```
The result agrees with the conclusion from part a.


c.
```{r}
lm1 <- lm(rep ~ A_F*B_F*C_F)
summary(lm1)
```
We can further reduce the model.
```{r}
lm1 <- lm(rep ~ A_F+B_F+C_F+A_F:C_F)
summary(lm1)
```

REGRESSION eqn: rep=27.167+ 9.167A+11.333B+15.667C-17.667AC

d.

```{r}
library(ggplot2)
qqnorm(m1$residuals)
qqline(m1$residuals)
```

There is no obvious violation of the assumptions.

e. 
```{r}
interaction.plot(A_F,C_F,rep)
```

I recommend the combination of LOW A, but high B,C levels.


6.5
a.

```{r}
A2 <- c(0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1)
B2 <- c(0,0,1,1,0,0,1,1,0,0,1,1,0,0,1,1)
vib <- c(18.2,27.2,15.9,41,18.9,24,14.5,43.9,12.9,22.4,15.1,36.3,14.4,22.5,14.2,39.9)
d2 <- data.frame(cbind(A2,B2), stringsAsFactors = TRUE)
m2 <- aov(vib ~ A2*B2, data = d2)
summary(m2)
```

Both A and B are effective. Besides, the interaction is also effective.

b.
```{r}
normalplot <- function(y, label=F,  n=length(y), fac.names=NULL, xlim=c(-2.2, 2.2), main="Normal Plot", ...)
  { # label the most singificant n effects
    m <- length(y)
    x <- seq(0.5/m, 1.0-0.5/m, by=1/m)
    x <-  qnorm(x)
    y <-  sort(y)
    qqplot(x, y, xlab="normal quantiles", ylab="effects",  xlim=xlim, main=main, ...)
    if(is.null(fac.names)) fac.names <-  names(y)
    else fac.names <-  rev( c(fac.names, rep("", length(y)-length(fac.names)) ) )
 
    ord=order(abs(y))
    if(label) for(i in ord[(m-n+1):m]) text(x[i]+.35,y[i], fac.names[i])  
}
normalplot(m2$residuals)
qqnorm(m2$residuals)
qqline(m2$residuals)
```
```{r}
plot(m2$residuals~m2$fitted.values)
abline(h=0, col="red")
```

The model seems to satisfy the assumptions, there is no obvious violation.

c.

```{r}
interaction.plot(A2,B2,vib)
```


I recommend the combination of low A and B levels.

a.
```{r}
temp <- rep(c(0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1),2)
titan <- rep(c(0,0,1,1,0,0,1,1,0,0,1,1,0,0,1,1),2)
heat <- rep(c(0,0,0,0,1,1,1,1,0,0,0,0,1,1,1,1),2)
grain <- rep(c(0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1),2)
cracks <- c(7.037,14.707,11.635,17.273,10.403,4.368,9.360,13.440,8.561,16.867,13.876,19.824,11.846,6.125,11.190,15.653,6.376,15.219,12.089,17.815,10.151,4.098,9.253,12.923,8.951,17.052,13.658,19.639,12.337,5.904,10.935,15.053)
d3 <- data.frame(cbind(temp,titan,heat,grain,cracks), stringsAsFactors = TRUE)
lm3 <- lm(cracks ~ temp*titan*heat*grain, data = d3)
summary(lm3)
```
All four factors seem to be effective, the interactions temp:titan,temp:heat,titan:heat, and temp:titan:heat also appear to be effective.

b.


```{r}
m3 <- aov(cracks ~ temp*titan*heat*grain, data = d3)
summary(m3)
```


All four factors seem to be effective, the interactions temp:titan,temp:heat, and temp:titan:heat also appear to be effective.

c.

```{r}
lm3n <- lm(cracks ~ temp+titan+heat+grain+temp:titan+temp:heat+temp:titan:heat, data = d3)
summary(lm3n)
```
cracks=8.2731+6.7093temp+2.0418titan+0.4115heat+1.9578grain+0.6347temp:titan-11.2490temp:heat+6.4670temp:titan:heat

d.

```{r}
normalplot(m3$residuals)
```

```{r}
plot(m3$residuals~m3$fitted.values)
abline(h=0, col="red")
```

The model seems to satisfy the assumptions, there is no obvious violation.


f.


```{r}
par(mfrow=c(2,3))
interaction.plot(temp, rep(1, length(cracks)), cracks)
interaction.plot(titan, rep(1, length(cracks)), cracks)
interaction.plot(heat, rep(1, length(cracks)), cracks)
interaction.plot(grain, rep(1, length(cracks)), cracks)
interaction.plot(temp,titan,cracks)
interaction.plot(temp,heat,cracks)
par(mfrow=c(1,1))
```

I recommend low level of A,B, and D, but high C.

7.1

```{r}
shift <- as.factor(c(rep(1,8),rep(2,8),rep(3,8)))
m4 <- aov(rep~A_F*B_F*C_F+shift,data = d1) 
summary(m4)
```

The largest effects are for tool geometry(B), the cutting speed-cutting angle interaction(AC), and the cutting-angle(C).

7.4

Let cg,a,c,ab be block1 and c,ac,bc,acbc be block2.

```{r}

block <- as.factor(rep(c(1,1,1,1,2,2,2,2),3))
d5 <- data.frame(cbind(A_F,B_F,C_F,block,rep), stringsAsFactors = TRUE)
m5 <- aov(rep ~ A_F*B_F*C_F+block, data = d5)
summary(m5)
```


The largest effects are for tool geometry(B), the cutting speed-cutting angle interaction(AC), and the cutting-angle(C).


