---
title: "101HW6"
author: "JING LI"
date: "3/9/2017"
output: pdf_document
---

13.1

a.

```{r}
part <- rep(c(1:10),6)
operator <- c(rep(1,30),rep(2,30))
measurement <- c(50,52,53,49,48,52,51,52,50,47,49,52,50,51,49,50,51,50,51,46,50,51,50,50,48,50,51,49,50,49,50,51,54,48,48,52,51,53,51,46,48,51,52,50,49,50,50,48,48,47,51,51,51,51,48,50,50,50,49,48)
m1.aov <- aov(measurement ~ factor(part) * factor(operator))
summary(m1.aov)
```
```{r}
MSA <- 11.002
MSB <- 0.417
MSAB <- 0.602
MSE <- 1.5
#part
1-pf(MSA/MSAB,9,9)
#operator
1-pf(MSB/MSAB,1,9)
#interaction
1-pf(MSAB/MSE,9,40)
```

Treatment part appears to be significant, while operator and interaction are not.

b.
```{r}
sigma <- MSE
sigma_tao <- (MSA-MSAB) / (2*3)
sigma_beta <- (MSB-MSAB) / (10*3)
sigma_tao_beta <- (MSAB-MSE) / (3)
sigma
sigma_tao
sigma_beta
sigma_tao_beta
```

Since both operator and the interaction terms are not significant, we can just assume that variances are 0.

13.2

a.

```{r}
part <- rep(c(1:10),9)
inspector <- c(rep(1,30),rep(2,30),rep(3,30))
testdata <- c(37,42,30,42,28,42,25,40,25,35,38,41,31,43,30,42,26,40,25,34,37,43,31,42,29,43,27,40,25,34,41,42,31,43,29,45,28,43,27,35,41,42,31,43,30,45,28,42,29,35,40,42,31,43,29,45,30,42,28,34,41,43,29,42,31,44,29,43,26,35,42,42,30,42,29,46,27,43,26,34,41,43,28,42,29,45,27,41,26,35)
m2.aov <- aov(testdata ~ factor(part)*factor(inspector)) 
summary(m2.aov)
```

```{r}
MSA <- 437.3
MSB <- 19.6
MSAB <- 2.7
MSE <- 0.5
#part
1-pf(MSA/MSAB,9,18)
#inspector
1-pf(MSB/MSAB,2,18)
#interaction
1-pf(MSAB/MSE,18,60)
```
Both treatments have significant effects, as well as the interaction term.

b.

```{r}
sigma <- MSE
sigma_tao <- (MSA-MSAB) / (3*3)
sigma_beta <- (MSB-MSAB) / (10*3)
sigma_tao_beta <- (MSAB-MSE) / (3)
sigma
sigma_tao
sigma_beta
sigma_tao_beta
```

14.1

```{r}
process <- c(rep(1,12),rep(2,12),rep(3,12))
batch <- rep(c(1,1,1,2,2,2,3,3,3,4,4,4),3)
burningrate <- c(25,30,26,19,28,20,15,17,14,15,16,13,19,17,14,23,24,21,18,21,17,35,27,25,14,15,20,35,21,24,38,54,50,25,29,33)
m3 <- lm(burningrate ~ factor(process)/factor(batch))
anova(m3)
```

```{r}
MSA <- 338.03
MSAB <- 230.84
MSE <- 18.92 
#process
1-pf(MSA/MSAB,2,9)
#batch
1-pf(MSAB/MSE,9,24)
```
From the results, we can conclude that the process is not significantly affecting burning rate, while batches are significant.


14.2

```{r}
machine <- c(rep(1,6),rep(2,6),rep(3,6),rep(4,6))
operator <- rep(c(1,1,2,2,3,3),4)
testdata <- c(79,62,94,74,46,57,92,99,85,79,76,68,88,75,53,56,46,57,36,53,40,56,62,47) 
m4 <- lm(testdata ~ factor(machine)/factor(operator))
anova(m4)
```

```{r}
MSA <- 1205.89 
MSAB <- 352.21
MSE <- 84.5 
#machine
1-pf(MSA/MSAB,3,8)
#operator
1-pf(MSAB/MSE,8,12)
```
From the results, we can conclude that the machine is not significantly affecting the output, while operator is significant.

14.20

```{r}
day <- as.factor(c(rep(1,12),rep(2,12),rep(3,12)))
appmethod <- as.factor(rep(c(1,2,3),12))
mix <- as.factor(rep(c(1,1,1,2,2,2,3,3,3,4,4,4),3))
testdata <- c(64.5,68.3,70.3,66.3,69.5,73.1,74.1,73.8,78,66.5,70,72.3,65.2,69.2,71.2,65.0,70.3,72.8,73.8,74.5,79.1,64.8,68.3,71.5,66.2,69.0,70.8,66.5,69.0,74.2,72.3,75.4,80.1,67.7,68.6,72.4)
m5 <- lm(testdata ~ day*appmethod*mix)
anova(m5)
```

```{r}
#appmethod
1-pf(111.047/0.491,2,4)
#mix
1-pf(102.493/0.755,3,6)

1-pf(1.673/0.732,6,12)
```

Both treatments have significant effects on the results. Interaction is slightly significant. The whole-plot error is less than subplot error, so there is less variation within the whole-plot.