---
title: "Stat101B Final Report"
author: "Gang Xu, Jing Li, Hun Chung, Dingrui Xue"
date: "3/19/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

    
    Civilization can???t exist without agriculture. So we want to study the agricultural environment on the islands and help farmers decide which field
and what kind of fertilizer and how much fertilizer they should use in order
to maximize the crops yields. 

    To be more specific, we want to study at which levels of each fertilizer,
nitrogenous and phosphatic, the crops produce maximum yields. We suspect that
the higher the level of both fertilizers, the more yields the plants will
produce.

    We are going to conduct a completely randomized two-factor factorial design
with blocking. We have two treatments, each with three levels: we label
concentration level 1 as low level, concentration level 3 as medium, and
concentration level 5 as high level. Our response variable is yield of plant.
Our nuisance factors are temperature, rainfall, climate and environment of
field. To roll out the effects of nuisance factors, we consider each field as a
block: Biruwa, Hofn and Matalau.

    All plants are randomly assigned to one of the fertilizer combinations. 
We are going to have 3 replicates. We use R Studio to generate 27 random numbers
from 1 to 27 without replacement. We label them Treatment 1-27. We assign same
treatment combination to Treatment n, n+9, and n+18. (0<n<10). After they
mature, we harvest all of them and count the fruits produced by each plant.

    
    #R codes for entering data and design 
    
```{r}
# R codes for generating random numbers
set.seed(12345)
sample(1:27, replace = F)
set.seed(22345)
sample(1:27, replace = F)
set.seed(32345)
sample(1:27, replace = F)

hofn<-c(119,145,180,141,142,150,138,153,148,194,133,160,160,135,170,151,157,
        165,122,163,162,195,131,160,143,115,148)
biruwa<-c(140,191,157,194,198,198,211,170,176,177,178,180,207,140,166,173,
          183,162,154,124,116,127,143,123,194,207,169)
matalau<-c(255,257,240,263,252,256,257,222,289,201,219,275,246,270,194,242,
           206,199,247,247,223,195,193,201,238,222,239)

hofnN<-c(1,3,5,3,1,3,5,5,3,5,1,1,1,5,3,3,3,5,1,5,3,5,1,5,3,1,1)
hofnP<-c(3,3,5,1,3,1,1,3,3,5,1,5,5,3,5,1,3,1,3,3,5,5,1,1,5,1,5)
biruwaN<-c(1,5,1,3,5,5,5,1,3,5,3,3,5,1,3,1,5,1,3,1,1,3,5,3,3,5,1)
biruwaP<-c(1,3,3,5,3,3,5,5,3,1,3,3,5,1,1,5,1,3,5,3,1,1,1,1,5,5,5)
matalauN<-c(3,5,1,5,5,3,3,1,1,5,3,5,3,5,1,5,1,3,3,5,1,1,3,3,5,1,1)
matalauP<-c(5,3,5,3,5,5,5,3,1,5,3,5,3,3,1,1,5,1,3,1,1,3,1,1,1,3,5)
block<- as.factor(c(rep(1,27),rep(2,27),rep(3,27)))
N<-as.factor(c(hofnN,biruwaN,matalauN))
P<-as.factor(c(hofnP,biruwaP,matalauP))
results<-c(hofn,biruwa,matalau)
Cashmeoutside<-data.frame(Nitrogen=N,Phosphate=P,Block=block,Results=results)
head(Cashmeoutside)
```

    Now we do an exploratory analysis
    
    
```{r}
library(ggplot2)
ggplot(Cashmeoutside, aes(y = Cashmeoutside$Results, x = Cashmeoutside$Nitrogen)) +
geom_boxplot(aes(fill = Cashmeoutside$Phosphate)) + facet_wrap(~ Cashmeoutside$Block)
```
    X-axis is Nitrogen Level. Y-axis is crop yields. 1,2,3 are the three blocks
we use, which are Biruwa, Hofn and Matalau fields. The three colors are
different phosphate level.
    
    We can see from the boxplot that fruit yields are significantly different on
different islands. We suspect that blocking variable has a great effect on fruit
yields. It seems that the treatments also have significant effect on fruit
yields.
    
    Then we go on and conduct ANOVA Analysis:
    
```{r}
m1 <- aov(Results ~ factor(Nitrogen)*factor(Phosphate)+factor(Block),data=Cashmeoutside)
summary(m1)
```
    From the ANOVA, we conclude that both nitrogen and phosphate have
significant effects on plant growth due to small p-value( less than 0.05). The
blocks also differ significantly due to small p-value. However, the ANOVA table
does not suggest a significant interaction effect. There is little interaction
between Nitrogen and Phosphate.
    
    Then we check if the assumptions of normality are met:
    
```{r}
plot(m1$residuals ~ m1$fitted.values)
qqnorm(m1$residuals)
qqline(m1$residuals)
```

    There is nothing unusual since the residual plot seems scattered and
patternless.Normality is satisfied since most points of the normal Q-Q plot
follows a straight line.
    
    Next we exmain interaction between two treatments by looking at the
interaction plot and main effects plot 
    
    
```{r}
interaction.plot(Cashmeoutside$Nitrogen,Cashmeoutside$Phosphate,
                 Cashmeoutside$Results,xlab="Nitrogen",ylab="Results",
                 trace.label = "Phosphate")


```
    At low level of both treatments, there is some interaction effects. But at
high level, the lines are almost parallel, suggesting little interaction
effects. The interaction plot suggests us to set both phosphate and nitrogen at
high level in order to get higher yields.
    
    Since we don't have significant interaction effects, we go on and examine
the main effects.
    
    
```{r}
par(mfrow = c(1,2))
interaction.plot(N, rep(1, length(results)), results, ylim=c(160, 220),legend=F,
								 main="Nitrogen Effect", ylab = "Yields", xlab = "Nitrogen")

interaction.plot(P, rep(1, length(results)), results, ylim=c(160, 220),legend=F,
								 main="Phosphate Effect", ylab = "Yields", xlab = "Phosphate")
```

    Both main effects nitrogen and phosphate are significant, but there is no
interaction between factors. So, we focus on main effect plots. In main effect
plots, as level of  factors increases, the yield increases. 

    Based on the above ANOVA analysis and Interaction plot analysis we can see
that both treatments have significant effects on crop yields. The higher the
concentration level, the more yields the crops produce. Also the yields are
significantly different for each fields. We have maximum yields on Matalau field
which is on the south-most island. There is no significant interaction effect
between nitrogenous concentration level and phosphatic concentration level.
Thus, we conclude that in order to maximize crop yields, famers should plant
crops on south-most island and use both fertilizers at high level. 

    There is also room to improve our experiment. For example we can take
rainfall or season into consideration. 
